\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{color}

\newcommand{\todo}[1]{{\color{red}\ TODO: {#1}}}

\setlength{\droptitle}{-12em}
\title{Research in Computer Science}
\date{Spring Semester 2017}
\author{Prof. Srdjan Capkun, Dr. Arthur Gervais}

\begin{document}
\maketitle

\section{Agreement}
The student undertaking this project work will be Mr. Rami Khalil (Legi-Nr. 16-932-568) for the duration of the Spring Semester in 2017 under the supervision of Prof. Srdjan Capkun and Dr. Arthur Gervais.

\section{Task Description}
Within the last decade, blockchain technology has emerged as a means of establishing a secure decentralized payment system. Crypto-currencies such as Bitcoin, Ethereum and others have gained much traction and acceptance across the world. However, these systems derive their security from wide replication across thousands of machines, and can not easily scale to meet the performance of today's centralized payment systems such as those backing credit and debit cards.

The student will be tasked with examining the state of the art in a new emerging technology based on blockchains called Payment Channels, which address some of the aforementioned scalability problems, and with suggesting and implementing improvements to current proposed payment channel designs and literature.

\vspace{5em}

\begin{tabular}{c c c}

Prof. Srdjan Capkun & Dr. Arthur Gervais & Rami Khalil \\
\\

\underline{\hspace{4cm}} & \underline{\hspace{4cm}} & \underline{\hspace{4cm}} \\

\end{tabular}

\end{document}